HL-LHC Computing Review:\\Common Tools and Community Software

### 2020-08-20 LHCC/2020/2020-01/input_generators.tex
Infrastructure and fixes
Add a Makefile that regenerates the document

Add a footnote hyperlink to mail the HSF editorial secretariat
Update LaTeX footnotes to symbols to avoid clashing with authors

Remove some spurious unicode (fi ligature) from generators text

\paragraph{Filtering inefficiency.} An additional large source of inefficiency
is due to the way the experiments simulate some processes, where they
generate large inclusive event samples, which are then ﬁltered on
ﬁnal-state criteria to decide which events are passed on to detector
simulation and reconstruction (e.g. CMS simulations of specific
$\Lambda_{B}$ decays have a 0.01\% efficiency and ATLAS B-hadron
filtering has \textasciitilde10\% efficiency for V+jets). This
inefficiency could be reduced by developing ﬁltering tools within the
generators themselves, designed for compatibility with the requirements
of the experiments. Filtering is an area where LHCb has a lot of
experience and already obtained significant speedups through various
techniques. The speed of colour reconnection algorithms is a limiting
factor for simulating rare hadron decays in LHCb.

>>>>

\paragraph{Filtering inefficiency.} An additional large source of inefficiency
is due to the way the experiments simulate some processes, where they
generate large inclusive event samples, which are then filtered on
final-state criteria to decide which events are passed on to detector
simulation and reconstruction (e.g. CMS simulations of specific
$\Lambda_{B}$ decays have a 0.01\% efficiency and ATLAS B-hadron
filtering has \textasciitilde10\% efficiency for V+jets). This
inefficiency could be reduced by developing filtering tools within the
generators themselves, designed for compatibility with the requirements
of the experiments. Filtering is an area where LHCb has a lot of
experience and already obtained significant speedups through various
techniques. The speed of colour reconnection algorithms is a limiting
factor for simulating rare hadron decays in LHCb.
